Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
passive to active

The model molten salt
reactor is based on the \gls{MSRE}. When developing new physics or investigating
different types of transients, the model problem can be reduced to a two
dimensional axisymmetric one for rapid proof of concept. To approximately simulate the lattice
structure of the \gls{MSRE} under 2D conditions, a geometry is constructed with 14 repeating
fuel-moderator regions, as shown in \Cref{fig:geom}. The fuel and moderator
radii are chosen such that the resulting area/volume fraction of fuel is .225 as
for the \gls{MSRE}.

@@

The fuel composition is based on the \gls{BOL} enriched uranium composition in the \gls{MSRE}
and is given in \Cref{table:comp} \cite{robertson_msre_1965}.

\begin{table}[htpb]
  \begin{center}
    \begin{tabular}{l | r}
      Component & Mass Fraction\\\hline\hline
      Li-7 & .1090\\
      Li-6 & 5$\times$10$^{-6}$\\
      F-19 & .6680\\
      Be-9 & .0627\\
      U-235 & .0167\\
      U-238 & .0344\\
    \end{tabular}
  \end{center}
        \caption{Fuel salt composition is based on the \gls{BOL} enriched
        uranium composition in the \gls{MSRE} design
        \cite{robertson_msre_1965}.}
  \label{table:comp}
\end{table}

@@

Group fluxes are shown in \Cref{fig:group1,fig:group2}. The effect of the vacuum
boundary conditions is shown by the cosinusoidal shapes in radial and
axial directions. Both the fast and thermal fluxes are striated, with
the fast group preferring the fuel and the thermal group preferring the moderator.

>>>>

The model molten salt reactor closely emulates the \gls{MSRE}. When developing new physics or investigating
different types of transients, the model problem can be reduced to a two
dimensional axisymmetric one for rapid proof of concept. To approximately simulate the lattice
structure of the \gls{MSRE} under 2D conditions, a geometry is constructed with 14 repeating
fuel-moderator regions, as shown in \Cref{fig:geom}. The fuel and moderator
radii are chosen such that the resulting area/volume fraction of fuel is .225 as
for the \gls{MSRE}.

@@

The model fuel composition is the \gls{BOL} enriched uranium composition in the 
\gls{MSRE} and is given in \Cref{table:comp} \cite{robertson_msre_1965}.

\begin{table}[htpb]
  \begin{center}
    \begin{tabular}{l | r}
      Component & Mass Fraction\\\hline\hline
      Li-7 & .1090\\
      Li-6 & 5$\times$10$^{-6}$\\
      F-19 & .6680\\
      Be-9 & .0627\\
      U-235 & .0167\\
      U-238 & .0344\\
    \end{tabular}
  \end{center}
        \caption{Fuel salt composition is the \gls{BOL} enriched
        uranium composition in the \gls{MSRE} design
        \cite{robertson_msre_1965}.}
  \label{table:comp}
\end{table}

@@

Group fluxes are shown in \Cref{fig:group1,fig:group2}. The cosinusoidal shapes in radial and
axial directions are caused by the vacuum boundary conditions. Both the fast and thermal fluxes are striated, with
the fast group preferring the fuel and the thermal group preferring the moderator.
